---
title: "Using Accelerometers to Categorize Deer Behavior"
teaching: 45
exercises: 0
source: Rmd
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
source("../bin/chunk-options.R")
knitr_fig_path("01-overview-")
```

## Using Tri-axial Accelerometion to Predict Behaviors

In this lesson, we use acceleration values collected in 3 dimensions (front/back, left/right, up/down) to categorize behavior of free-ranging deer. 

steps:
- "Extract ACC data from hard drives"
- "Annotate video behaviors"
- "Merge video and ACC by date/time stamp"
- "Merge/collapse behavior categories as needed"
- "Subset data to simplest case: Pure/single behaviors only"
- "Separate static & dynamic acceleration using filter"
- "Convert dynamic acceleration to frequency domain" - find references
- "Split into training, validation, and test data"
- "PCA on training data"
- "Use PCs in logistic regression"
- "Rotate/project (note: apply same scaling/centering as was used in training)"
- "Use logistic regression model to ???"
